---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# circRNAprofiler: an R-based computational framework to explore expression, genomic context, and function of circular RNAs 

circRNAprofiler is an R-based framework that that only requires an R installation
and offers 15 modules for a comprehensive in silico analysis of circRNAs. 
This computational framework allows to combine and analyze circRNAs previously
detected by multiple publicly available annotation-based circRNA detection tools.
It covers different aspects of circRNAs analysis from differential expression
analysis, evolutionary conservation, biogenesis to functional analysis.  
The pipeline used by circRNAprofiler is highly automated and customizable,
different species and genome assemblies can be used. Furthermore, circRNAprofiler
includes additional plotting functions for the visualization of the data 
which facilitate the interpretation of the results.

## Installation

You can install the released version of circRNAprofiler using the devtools
package. To do so:

```{r, eval = FALSE}
install.packages("devtools")
library(devtools)
install_github("Aufiero/circRNAprofiler")
```

## Documentation
Detiled information on using this package can be found in the package vignettes.

```{r, eval = FALSE}
browseVignettes("circRNAprofiler")
```


## Bugs and Issues
We work hard to ensure that circRNAprofiler is a powerful tool empowering your
research. However, no software is free of bugs and issues, therefore we would 
love to get feedback from our users.


