---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![HitCount](http://hits.dwyl.io/Aufiero/circRNAprofiler.svg)](http://hits.dwyl.io/Aufiero/circRNAprofiler) 

# circRNAprofiler: an R-based computational framework for the downstream analysis of circular RNAs

circRNAprofiler is an R-based framework that only requires an R installation
and offers 15 modules for a comprehensive in silico analysis of circRNAs. 
This computational framework allows to combine and analyze circRNAs previously
detected by multiple publicly available annotation-based circRNA detection tools.
It covers different aspects of circRNAs analysis from differential expression
analysis, evolutionary conservation, biogenesis to functional analysis. The 
pipeline used by circRNAprofiler is highly automated and customizable. Furthermore,
circRNAprofiler includes additional functions for data visualization which 
facilitate the interpretation of the results.

## Installation

You can install circRNAprofiler from Bioconductor using:
```{r, eval = FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("circRNAprofiler")
```

To download the latest development version on github use:
```{r, eval = FALSE}
BiocManager::install("Aufiero/circRNAprofiler")
```

## Documentation
Detailed information on using this package can be found in the package vignettes:

```{r, eval = FALSE}
browseVignettes("circRNAprofiler")
```

## Bugs and Issues
We work hard to ensure that circRNAprofiler is a powerful tool empowering your
research. However, no software is free of bugs and issues, therefore we would 
love to get feedback from our users.

## Citation
If you find this code useful in your research, please cite:

Aufiero, S., Reckman, Y.J., Tijsen, A.J. et al. circRNAprofiler: an R-based computational framework for the downstream analysis of circular RNAs. BMC Bioinformatics 21, 164 (2020). https://doi.org/10.1186/s12859-020-3500-3
